SAT Competition 2020\tnoteref{title}

### 2020-11-17 paper/main.tex
prepared paragraphs for descriptions of winning solvers

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{tkz-graph}
\usepackage{lscape}

@@

@@

% Stack a variable number of arguments:
\makeatletter
\newcommand{\stack}[1]{%
    \begin{tabular}{@{}l@{}}#1\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
\makeatother

\begin{table}[h]
\begin{tabular}{|l|l|l|}
\hline
Team & Solver & Configuration / Variant / Hack \\
\hline

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} 
 & \multirow{3}{*}{Kissat-sc2020} & --\\
 &  & sat\\
 &  & unsat\\
\cline{2-3}
 & Cadical-sc2020 & --\\
\hline

\multirow{3}{*}{Zhang, Cai}
 & \multirow{3}{*}{Relaxed\_LCMDCBDL} & --\\
 &  & noTimeParam\\
 &  & newTech\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
 & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
 &  & lsids\\
\hline

\stack{Soos, Selman, }{Kautz}~ & CryptoMiniSat-WalkSAT & -- \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 & \multirow{3}{*}{Cadical} & trail\\
 &  & alluip\\
 &  & alluip-trail\\
 \cline{2-3}
 & Maple-LCM-Dist & alluip-trail\\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc\\
 & & f2trc-s\\
 \cline{2-3}
 & MapleLCMDistChronoBT-DL & f2trc\\
\hline

\stack{Kochemazov, }{Zaikin, }{Kondratiev, }{Semenov} ~& MapleLCMDistChronoBT-DL-v3 & --\\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}} & \multirow{4}{*}{Undominated-LC-MapleLCMDistChronoBT-DL} & --\\
 &  & top16\\
 &  & top24\\
 &  & top36\\
\hline

\multirow{5}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{Painless-ExMapleLCMDistChronoBT} & padc\_dl\\
 &  & padc\_dl\_ovau\_lin\\
 &  & padc\_dl\_ovau\_exp\\
 &  & psids\_dl\\
 \cline{2-3}
 & Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & DurianSat & --\\
\hline

\multirow{2}{*}{Chen}
 & Maple & Mix\\
 & Maple & Simp\\
\hline

Riveros & SLIME & --\\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen} & MLCMDChronoBT-DL-Scavel & --\\
 & MapleLCMDistChronoBT-DL-Scavel01 & --\\
 & MapleLCMDistChronoBT-DL-Scavel02 & --\\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & MapleCOMSPS\_LRB\_VSIDS\_2 & --\\
 & MapleCOMSPS\_LRB\_VSIDS\_2 & LRB\_VSIDS\_2\_init\\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
 & exp-V-L-MLDCBT-DL & --\\
 & exp-L-MLD-CBT-DL & -- \\
 & exp-V-MLD-CBT-DL & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{3}{*}{MapleCM} & +dist \\
 &  & +dist+sattime2s+- \\
 &  & +dist+simp2-- \\
 & MapleCMused & +dist \\
\hline

Kaiser, Hartung & PauSat & -- \\
\hline

Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
\hline
\end{tabular}
\caption{Teams, Solvers and Hacks participating in the Main Tracks}
\end{table}

\subsection{Planning Track}

@@

@@

@@

@@

GBD Tools is a new tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}

@@

\section{Competition Results}

\todo{for each track summarize the descriptions of the winning solvers}

>>>>

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{multirow,makecell}
\usepackage{float,lscape}
\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
\usepackage{tkz-graph}
\usepackage{lscape}

@@

\subsection{Main Tracks}

This year in the Main Track, we had a Planning Sub-Track. 
The general idea is, that next to a balanced selection of benchmark instances in main track, to each year also offer one domain-specific sub-track.

@@

% Stack a variable number of arguments:
\makeatletter
\newcommand{\stack}[1]{%
\begin{tabular}{@{}l@{}}#1\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
\makeatother

\definecolor{gold}{HTML}{FFF3D6}
\definecolor{silver}{HTML}{F3F5F7}
\definecolor{cupper}{HTML}{EAD9D7}
\fboxsep0pt
\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}

\begin{table}[h!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Variant & \bf Award \\
\hline

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat-sc2020} &  -- & \firsto\firstu\\
 &  &  sat & \firsto\firstu\seconds\\
 &  &  unsat & \firstu\thirdp\\
\cline{2-4}
 &  Cadical-sc2020 &  -- & \\
\hline

\multirow{3}{*}{Zhang, Cai}
    & \multirow{3}{*}{MapleLCMDistCBT-DL} & Relaxed & \\
 &  & Rel. noTimeParam & \\
 &  & Rel. newTech & \secondo\firsts\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{CryptoMiniSat-CCAnr} &  -- & \thirdo\thirds\secondp\\
 &  &  lsids & \thirdo\thirds\secondp\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & CryptoMiniSat-WalkSAT & -- & \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  trail & \secondu\\
 &  &  alluip & \firstp\\
 & \multirow{-3}{*}{Cadical} &  alluip-trail & \firstp\\
 \cline{2-4}
 & MapleLCMDist & alluip-trail & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc & \\
 & & f2trc-s & \thirdu\\
 \cline{2-4}
 & MapleLCMDistCBT-DL & f2trc & \\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& MapleLCMDistCBT-DL-v3 & -- & \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{MapleLCMDistCBT-DL-v3} & Undominated & \\
 &  & Undom. Top16 & \\
 &  & Undom. Top24 & \\
 &  & Undom. Top36 & \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{ExMapleLCMDistChronoBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & DurianSat & -- & \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{MapleLCMDistCBT-DL} & Maple\_Mix & \\
 &  & Maple\_Simp & \\
\hline

Riveros & SLIME & -- & \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{MapleLCMDistCBT-DL} & Scavel & \\
 &  & Scavel01 & \\
 &  & Scavel02 & \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{MapleCoMsPS\_LRB\_VSIDS\_2} & -- & \\
 &  & init & \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{MapleLCMDistCBT-DL-v2.2} & exp-V-LGB & \\
 &  & exp-V-L & \\
 &  & exp-L & \\
 &  & exp-V & \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{MapleCM} & \texttt{+}dist & \\
 &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} & \\
 &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} & \\
 &  & used\texttt{+}dist & \\
\hline

Kaiser, Hartung & PauSat & -- & \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{ParaFROST} & -- & \\
 &  & CBT & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack). 
Note that many teams are only responsible for the variant of a previously existing base solver.
Awards were given in Main (m), SAT (s), UNSAT (u), and Planning (p) sub-tracks.}
\end{table}

@@

\begin{table}[h]
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Awards\\
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
 & P-MCOMSPS-STR-64 & \firsto \\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & Plingeling & \secondo \thirds \firstu \\
 & Treengeling & \\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & ManyGlucose-32 & \thirdo \thirdu \\
 & ManyGlucose-64 & \thirdu \\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & painlessmaplevone & \seconds \\
 & painlessmaplevtwo & \seconds \\
\hline
Li, Wu, Xu, Chen & syrupscavel & \\
\hline
Chen & abcdsatptwenty & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the parallel track.}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

@@

GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}

@@

\section{Competition Results}
\todo{for each track summarize the descriptions of the winning solvers}

\paragraph{Kissat} 
three configurations submitted, four awards won, cdcl by several mixed strategies

\paragraph{CryptoMiniSat-CCAnr}
two variants: with and without lsids, with lsids slightly better, three awards won,  combination of cdcl and sls

\paragraph{Cadical Hack}
three configurations, two awards

\paragraph{MapleLCMDistCBT-DL Relaxed newTech}
this variant won two awards

\paragraph{MapleLCMDistCBT f2trc-s}
this variant won onw awards

\subsection{Incremental Library Track}
\paragraph{Cryptominisat-5}

\paragraph{P-MCOMSPS-STR} three awards

\paragraph{Plingeling} three awards

\paragraph{ManyGlucose} two awards

\paragraph{Painless Maple} one award

\paragraph{Mallob Mono}

\paragraph{TopoSAT 2}

\paragraph{Slime}
